Cosmological constraints from the redshift dependence of the Alcock-Paczynski effect: significant improvement in the dark energy figure of merit

### 2017-09-27 Draft/Draft1.2.tex
minor changes

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
while improving upon earlier works \citep{Li2016},
we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
allowing for competitive and unbiased constrains to be placed on cosmological parameters.
% The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
% We improve the methodology of \citep{Li2016} by significantly reducing its computation time, 
% which enables us to explore three or more cosmological parameters.
% We applied the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
We find that our results, in combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, yield
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
% We carefully checked the robustness of the results.
The AP method can %be combined with the standard BAO method,
greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=14cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=8-30 \rm Mpc/h$, 
   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
   excluding the last redshift bin in the analysis, 
   discarding the systematics correction, 
   or reducing the number of mocks in the estimation of covariance matrix,
   the results remain robust (black contours).
   }
\end{figure*}

@@

%\begin{figure*}
%   \centering{
%   \includegraphics[width=6cm]{fig_smu.eps}
%   \includegraphics[width=10.5cm]{fig_comp.eps}
%   }
%   \caption{\label{fig_method}
%   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
% The number counts are measured in the fiducial cosmology in a uniform grid (blue dashed.
%  Just for illustration; the grid adopted in real analysis is much denser).
% In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
% %due to the distortion of geometry,
% the distribution of number counts in $(s, \mu)$ space becomes the red solid grid ({\bf Check}).
% We utilize the mapping realtion to approximate the 2pCF in vaiours cosmologies, without re-conducting the 2pCF statistics. 
% Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
% Results obtained using the precise 2pCFs (gray filled) 
% and approximate 2pCFs (blue solid) 2pCFs matches each other quite well.
%   }
%\end{figure*}

@@

We performed a thorough test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our test is that the 
shift in contour position is very small even when %we do not include the systematic correction.
the systematics are not corrected.
%This is reassuring, since we may have worried that {\it cosmological dependence} 
%of the systematic correction could influence the final result. 
This indicates that, for the data analysis of current galaxy surveys,
the systematic effects in our method may not be important.
But it remains to be seen if this is true for future galaxy surveys,
or when the cosmology dependence of the systematics effects is taken into account.

@@

In recent studies we have proposed to constrain cosmological parameters 
governing the expansion history of the universe via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained a tight constraint 
on the CPL parametrization of dark energy.
%The derived cosmological constraints are fully consistent with a cosmological constant 
%dark energy component having no redshift evolution.

@@

>>>>

\begin{abstract}
We use the anisotropic clustering signal of 1,133,326 galaxies from the Sloan Digital Sky Survey Data Release 
12, spanning the redshift range $0.15<z<0.69$ to place constraints on the expansion history of the Universe. 
%Concentrating on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$,
%while improving upon earlier works \citep{Li2016},
%we present a novel use of the Alcock-Paczynski (AP) test via clustering difference between redshift bins on scales of 6-40 $h^{-1}\rm Mpc$.
%This differential measure is shown to be a robust statistical tool that mitigates many systematic effects, 
%allowing for competitive and unbiased constrains to be placed on cosmological parameters.
The Alcock-Paczynski (AP) test was performed via the redshift dependence of clustering on scales of 6-40 $h^{-1}\rm Mpc$.
We improve the methodology of \cite{Li2016} by significantly reducing its computation time. 
This enables us to efficiently explore three or more cosmological parameters.
We then apply the improved method on the Chevallier-Polarski-Linder parametrization of dark energy, $w=w_0+w_a\frac{z}{1+z}$.
In combination with the CMB, BAO, SNIa and $H_0$ from Cepheid data, we obtain
$\Omega_m = 0.301 \pm 0.008,\ w_0 = -1.042 \pm 0.067,\ w_a = -0.07 \pm 0.29$ (68.3\% CL). 
Adding our new AP measurements to the aforementioned results 
reduces the error bars by $\sim$30-40\%,
%and reduces the area of $w_0-w_a$ contour by 50\%.
and improves the dark energy figure of merit by a factor of 2. 
We checked the robustness of the results.
%The AP method may %be combined with the standard BAO method,
%greatly increase the power of ongoing and future galaxy surveys in probing dark energy.
\end{abstract}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=18cm,natwidth=6,natheight=5]{fig_con_tests.pdf}
   %\includegraphics[width=9cm,natwidth=4,natheight=4]{fig2b.pdf}
   %\includegraphics[height=8cm]{fig2b.pdf}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
   }
   \caption{\label{fig_contest}
   Robustness test of the results.
   For the ``default'' constraints (pink contours) are derived using six redshift bins, 
   $\mu_{\rm max}=0.97$, $n_{\mu}=15-20$, $s=6-40 \rm Mpc/h$,
   a fiducial cosmology $\Omega_m=0.26,\ w=-1.0$ for the measurement of 2pCF,
   systematic effects estimated from Horizon Run 4 simulations, 
   and covariance estimated using 2,000 MultiDark PATCHY mocks.
   When we alters one of these options by using $\mu_{\rm max}=0.99$, 
   $\mu_{\rm max}=0.85$, $n_{\mu}=15-20$, $s=8-30 \rm Mpc/h$, 
   a fiducial cosmology of $\Omega_m=0.26,\ w=-0.6$, 
   excluding the last redshift bin in the analysis, 
   discarding the systematics correction, 
   or reducing the number of mocks in the estimation of covariance matrix,
   the results remain robust (black contours).
   }
\end{figure*}

@@

\begin{figure*}
   \centering{
   \includegraphics[width=6cm]{fig_smu.eps}
   \includegraphics[width=10.5cm]{fig_comp.eps}
   }
   \caption{\label{fig_method}
   Left panel: Mapping $\xi(s,\mu)$ from the fiducial cosmology to four other cosmologies. 
 The number counts are measured in the fiducial cosmology in the blue dashed grid (for illustration purpose 
  the grid shown here is much sparser than the grid adopted in real analysis).
 In the four cosmologies with $(\Omega_m,w) = (0.31,-1.5),\ (0.31,-0.5),\ (0.41,-1.0)\ \rm and\ (0.21,-1.0)$, 
 %due to the distortion of geometry,
 the distribution of number counts in $(s, \mu)$ space becomes the red solid grid.
 We utilize the mapping realtion to infer the 2pCFs in vaiours cosmologies without re-conducting the 2pCF statistics. 
 Right panel: Cosmological constraints in the $\Omega_m$-$w_0$ plane, with the value of $w_a$ fixed as zero.
 Results obtained using the precise 2pCFs (gray filled) 
 and approximate 2pCFs (blue solid) 2pCFs agree with each other quite well.
   }
\end{figure*}

@@

We performed a test of all the possible variables in our methodology.
Fig.\ref{fig_contest} shows that 
the result is unaffected by the line-of-sight $\mu$-cut, 
the number of angular bins, 
the range of radial integration and the choice of fiducial cosmology. 
%we adopt $\mu_{\rm max}=0.99\ (0.85)$ to include more (less) regions near the LOS,
%decrease the number of angular bins to $n_{\mu}=15-20$,
%change the range of clustering to $8-30 \rm Mpc/h$,
%change the fiducial cosmology to $\Omega_m=0.26,\ w=-0.6$,
%exclude 1 or 2 high redshift bins,
%or reduce the number of mocks to 1000.
The result does not change significantly if we remove the highest redshift bin,
where the estimated systematics is comparably large.
The most striking point to note in our test is that the 
shift in contour position is not significant even when %we do not include the systematic correction.
the systematics are not corrected.
%This is reassuring, since we may have worried that {\it cosmological dependence} 
%of the systematic correction could influence the final result. 
This indicates that, for the data analysis of current galaxy surveys,
the systematic effects in our method may not be important.
But it remains to be seen if this is true for future galaxy surveys,
or when the cosmology dependence of the systematics effects is taken into account.

@@

In recent studies we have proposed to constrain cosmological parameters 
governing the expansion history of the universe via 
the redshift dependence of anisotropic galaxy clustering\cite{Li2016}.
This approach enables a robust AP test on relatively small scales.
In this paper we improved the methodology and obtained a tight constraint 
on the CPL parametrization of dark energy.
The derived cosmological constraints are fully consistent with a cosmological constant 
dark energy component having no redshift evolution.

@@

%Yet there are still issues demanding more investigations.
In this analysis, the systematic effects and the covariance matrices are estimated using simulations performed in a certain cosmology.
Their cosmological dependence needs to be investigated in future works to guarantee the robustness of the method.
